Simulating International Energy Security

### 2013-11-22 Writeups/CSS739 Paper/Paper.tex
Paper update

\subsection{Data Sources}
The model inputs are empirical whenever possible. Data inputs are: oil trade relationships, country political instability, and country consumption of domestic oil production. Total supply and demand are derived from input data.

@@

Political instability estimates are taken from the Economist Intelligence Unit's Political Index ratings \citep(eiu_2013). These are in turn estimated based on the methodology developed by the Political Instability Task Force \citep{goldstone_2005}, which could predict the onset of internal instability in a two-year period with 80\% accuracy. Thus, these scores are normalized such that a rating of 10 (the maximum) is associated with an 80\% probability of instability within a 24-month timeframe, translating into a [[FILLIN]] monthly probability of crisis onset.

>>>>

\subsection{Data Sources}
The model inputs are empirical whenever possible. Data inputs are: oil trade relationships, country political instability, and country consumption of domestic oil production. Total supply and demand are derived largely from input data.

@@

Political instability estimates are taken from the Economist Intelligence Unit's Political Index ratings \citep{eiu_2013}. These are in turn estimated based on the methodology developed by the Political Instability Task Force \citep{goldstone_2005}, which could predict the onset of internal instability in a two-year period with 80\% accuracy. Thus, these scores are normalized such that a rating of 10 (the maximum) is associated with an 80\% probability of instability within a 24-month timeframe, translating into a [[FILLIN]] monthly probability of crisis onset.

For the majority of countries, I assume that supply and demand are equal to total export and imports, respectively. For the top ten oil producers, I use US Energy Information Administration (EIA) estimates \citep{} for those countries' consumption of their own domestic production.

\subsection{Formal Description}

The model consists of \textbf{Country} agents, linked by two networks: a directed \textbf{trade network}, and an undirected \textbf{geographic adjacency} network, where the country agents are the network nodes.

Model variables may be \emph{data-derived}, \emph{parameters} that are fixed for each run and may be changed between them, or \emph{states} of the agents and edges that vary during the model.

\subsubsection{Agent Description}
